An FMI-Based Initialization Plugin for INTO-CPS Maestro 2

### 2020-07-01 background.tex
Updated background section

The interconnections of FMU variables can lead to circular dependencies between the variables. An example of this is presented in the example in \cref{sec:case_study}.

as seen in \cref{fig:fmu_cycle} showing a co-simulation scenario containing an algebraic loop and its Initialization Graph.
\claudio{Simon, can you update the above paragraph to use the co-simulation scenario presernted in the case study section? You can then reuse the space and the reader will already get some familiarity with the case study. Maybe you can even ditch the \cref{fig:fmu_cycle}.}

>>>>

The interconnections of FMU variables can lead to circular dependencies between the variables. An example of this behavior is the car suspension system that is presented in \cref{sec:case_study}. \cref{fig:fmu_cycle} shows the co-simulation scenario of the and the Initialization Graph of the system. The Initialization Graph in \cref{fig:fmu_cycle} is annotated with the strongly connected components.

### 2020-07-01 initializationorder.tex
Updated background section

In the \textit{Initialization Mode} state, all variables of all FMUs should be defined.
The parameters of each FMU are set first, and the order they are set is again insignificant as they are independent.
Afterwards the interconnected variables should be defined, but as stated by the \cref{def:feedthrough,def:getout,def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops places even more constraints on the initialization order. All these constraints must be satisfied by the initialization procedure of the interconnected variables.
\claudio{I feel like the previous two sentences are a bit contradictory, and are probably constructed like so because you did not deal with algebraic loops upfront. When algebraic loops are not there, there must be an order. But when algebraic loops are there, it's not that there's more constraints... it's just that one has to isolate the strong components from the rest. The result is then an order between strongly connected components, but no order within each component}

>>>>

In the \textit{Initialization Mode} state, all variables of all FMUs should be defined.
The parameters of each FMU are set first, and the order in which they are set is again insignificant as they are independent.
Afterwards the interconnected variables should be defined, but as stated by the \cref{def:feedthrough,def:getout,def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops place even more requirements on the initialization strategy. Since each non simple strongly connected components need to be isolated from the other parts on the system in able to apply the fixed point iteration technique.

%\%claudio{I feel like the previous two sentences are a bit contradictory, and are probably constructed like so because you did not deal with algebraic loops upfront. When algebraic loops are not there, there must be an order. But when algebraic loops are there, it's not that there's more constraints... it's just that one has to isolate the strong components from the rest. The result is then an order between strongly connected components, but no order within each component}
